
\usepackage{pdfpages}

\title{}
\documentclass[letterpaper, 11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} %clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}
%------ Heading -------

\begin{center}
  \textbf{\Huge \scshape Hamzah Mujawar} \\ \vspace{3pt}
  \small 
  \faMobile \hspace{.5pt} \href{tel:07501588303}{+44 0750 1588303}
  $|$ 
  \faAt \hspace{.5pt} \href{mailto:hamzah1faisal@gmail.com}{hamzah1faisal@gmail.com}
  $|$ 
  \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/hamzah-mujawar-7016b4238/}{LinkedIn}
  $|$
  \faGithub \hspace{.5pt} \href{https://github.com/jetthreat}{GitHub}
  $|$ 
  \faMapMarker \hspace{.5pt} \href{https://maps.app.goo.gl/a9FHvhXJpbpQzabT8}{Egham, United Kingdom}
\end{center}

%----- Education -----
\section{Education}
\vspace{3pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {Royal Holloway
      }{Egham, United Kingdom}
      {M.Sc. in Information Security}{Sep 2023 \textbf{--} \textit{Present}}


  \resumeSubHeadingListEnd



\vspace{-25pt}
  \resumeSubHeadingListStart
    
    \resumeEducationHeading
      {University of Wollongong in Dubai
      }{Dubai, United Arab Emirates}
      {B.Eng. in Computer Engineering;   \textbf{GPA: 3.62/4.00 (77.2\% Overall)}}{Sep 2019 \textbf{--} Jul 2023}
      \textbf{Dean's List(2022)}
        \resumeSubHeadingListStart
        \small{\item{
            \textbf{Notable Achievements:} $3^{rd}$ Highest Grade Within Batch; Appointed Laboratory Assistant for outstanding performance in practicals.}}
        \resumeSubHeadingListEnd


 \resumeSubHeadingListEnd





%----- Skills -------
\section{Skills}
\vspace{2pt}
\resumeSubHeadingListStart
  \small{\item{
      \textbf{Languages: }{C/C++, Java, Python, MATLAB.} \\ \vspace{3pt}
      \textbf{Technologies: }{Git, Linux, ROS, OpenCV, PyTorch, TensorFlow, LaTeX, MultiSim, UltiBoard.} \\ \vspace{3pt}
    }}
\resumeSubHeadingListEnd





%---- Work Experience -----
\section{Work Experience}
\vspace{3pt}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Wollongong in Dubai}{Dubai, United Arab Emirates}
      {Lab Assistant + Research and Development Intern}{March 2022 \textbf{--} Jul 2023}
      \resumeItemListStart
        \resumeItem{Assisted lab instructors in conducting experiments for laboratory sessions by setting up apparatus and providing detailed, step-by-step guidance.}
        \resumeItem{Assisted lab engineer in recording experiments for distance learning classes.}
        \resumeItem{Edited raw experiment recordings using Final Cut Pro}
        \resumeItem{Documented step-by-step instructions to fabricate PCBs using Ultiboard and Multisim.}
        \resumeItem{Conducted regular inspections to ensure the functionality of laboratory equipment; promptly addressed issues by either replacing or repairing faulty equipment to maintain optimal working conditions in the labs.}
      \resumeItemListEnd

    \resumeSubheading
      {Assembly @in5}{Dubai, United Arab Emirates}
      {Research and Development Intern}{August 2021 \textbf{--} December 2021}
      \resumeItemListStart
        \resumeItem{Worked on wiring and programming of automatic kinetic sand table on Arduino and Raspberry Pi boards to allow two-axis control using two stepper motors which allows for automatic pattern drawing using https://github.com/jeffeb3/sandify.}
        \resumeItem{Worked on a python script that takes camera input and projects it on an 80 by 80 LED matrix using a Raspberry Pi using OpenCV library.}
        \resumeItem{The above two projects were exhibited in the GITEX annual tech show at the Dubai World Trade Centre.}
        \resumeItem{Led a workshop on the introduction to linux and virtual machines https://youtu.be/8LXHlV4mwN4.}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

\section{Thesis}
\vspace{3pt}
  \resumeItemListStart
    \resumeItem{Comparative Analysis of SLAM and YOLO for Mobile Robot Navigation and Object Detection in Indoor and Urban Environments. \textbf{Available: }{https://github.com/hamzah-mujawar/Undergrad-Thesis}}
    \resumeItemListEnd

\section{Projects}
\vspace{-3pt}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{TensorFlow CNN Mood Detection for Music} $|$ \emph{\href{https://github.com/hamzah-mujawar/Mood_Detection_CNN_Using_Tensorflow}{\color{blue}GitHub}}}{}
      \resumeItemListStart
        \resumeItem{Has a preprocessor that converts .mp3 files into an MFCC using librosa python library.}
        \resumeItem{Has three Conv2D layers and a flatten and dense layer, and a final layer that scores the 4 categories: happy/relaxed/sad/angry.}
      \resumeItemListEnd
  \resumeProjectHeading
    {\textbf{Web-Based IoT System for Monitoring and Controlling Plant Growth Conditions}}
  
  \resumeProjectHeading
    {\textbf{Landing Page using CSS Flexboxes and HTML} $|$ \emph{\href{https://github.com/hamzah-mujawar/Landing-Page}{\color{blue}GitHub}}}{}





\resumeSubHeadingListEnd

\end{document}
